method

### 2022-02-10 06_Paper/ER-ED/Manuscript_ERED_Stage1.Rmd
fertsch

# Design Table

@@

>>>>

\newpage
```{r fig1appendix, echo = FALSE, message = FALSE, warning = FALSE, out.width="90%"}
include_graphics(here("99_Thinktank","other","Paradigm_Scheme_T2.png" ))
```
*Figure 1.* Exemplary visualisation of two response patterns. In the top half, the person has a clear preference for one of the three strategies. In the lower half, they have no clear preference and therefore show an inconsistent response pattern. This pattern can also be represented by our paradigm.
# Design Table

@@

\includepdf[pages={-}, landscape=true]{Supplement/StimList_Suppl.pdf}

## Pilot study: Subjective arousal in the conditions "active viewing - neutral" and "active viewing - negative"
ANOVA:

`r afex::nice(SubjArousalView_aov)%>% knitr::kable(x = .)` 
$BF10=$ `r round(extractBF(SubjArousalView_BF)$bf, digits = 2)`

Paired contrasts:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  SubjArousalView_con,
  caption = "Paired contrasts for the rmANOVA comparing subjective arousal of negative and neutral pictures in the condition \"active viewing\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```
Figure:
```{r FigSubjArousalViewPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - neutral\" and \"Active viewing - negative\" visualized as boxplots. Each dot represents the effort rating of a single subject. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigSubjArousalViewPilot)
```
## Pilot study: Subjective arousal in the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression"
ANOVA:
`r afex::nice(SubjArousalReg_aov)%>% knitr::kable(x = .)`
$BF10=$ `r round(extractBF(SubjArousalReg_BF)$bf, digits = 2)`

Paired contrasts:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  SubjArousalReg_con,
  caption = "Paired contrasts for the rmANOVA comparing subjective arousal of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```
Figure:
```{r FigSubjArousalRegPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective arousal ratings for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the effort rating of a single subject. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigSubjArousalRegPilot)
```
## Pilot study: Subjective effort in the conditions "Active viewing - negative", "Distraction", "Distancing", and "Suppression"
ANOVA:
`r afex::nice(SubjEffort_aov)%>% knitr::kable(x = .)`
$BF10=$ `r round(extractBF(SubjEffort_BF)$bf, digits = 2)`

Paired contrasts:
```{r, echo=FALSE, message=FALSE, warning=FALSE}
apa_table(
  SubjEffort_con,
  caption = "Paired contrasts for the rmANOVA comparing subjective effort of conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\".",
  note = "$SE$ = standard error, $df$ = degrees of freedom, $t$ = $t$-statistic, $p$ = $p$-value, CI = confidence interval.", 
  escape = FALSE,
  placement = "H"
)
```
Figure:
```{r FigSubjEffortPilot, echo=FALSE, message=FALSE, warning=FALSE, fig.cap="Subjective effort ratings for the conditions \"Active viewing - negative\", \"Distraction\", \"Distancing\", and \"Suppression\" visualized as boxplots. Each dot represents the effort rating of a single subject. Bold dots represent outliers.", fig.pos="H", out.width="75%"}

print(FigSubjEffortPilot)
```

### 2022-02-10 06_Paper/ER-ED/TheoreticalBackground.Rmd
fertsch

In the original study by Westbrook et al. [-@Westbrook2013], cognitive load was varied using the *n*-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli. 
Participants had to decide whether they wanted to repeat a higher *n*-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward. 
In the current study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest *n*-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies [@Scheffel2021].
Moreover, there is nothing like an objectively easiest ER strategy.
Therefore, we have to add an additional step, which preceeds the other steps and where the option with the higher subjective value is determined. 
In this step, the same monetary value (i.e., 1 EUR) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 EUR) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al. [-@Westbrook2013] until the indifference point is reached.
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see figure 1).
Additionally, we will test our adapted paradigm in a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al., ...).
```{r fig1, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Exemplary visualisation of two response patterns. In the top half, the person has a clear preference for one of the three strategies. In the lower half, they have no clear preference and therefore show an inconsistent response pattern. This pattern can also be represented by our paradigm."}
include_graphics(here("99_Thinktank","other","Paradigm_Scheme_T2.png" ))
```
## 1.2 The present study

@@

Exploratorily, we want to investigate whether individual SVs are related to personality traits.

>>>>

In the original study by Westbrook et al. [-@Westbrook2013], cognitive load was varied using the *n*-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli. 
Participants had to decide whether they wanted to repeat a higher *n*-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward. 
In the current study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest *n*-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies [@Scheffel2021].
Moreover, there is nothing like an objectively easiest ER strategy.
Therefore, we have to add an additional step, which preceeds the other steps and where the option with the higher subjective value is determined. 
In this step, the same monetary value (i.e., 1 EUR) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 EUR) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al. [-@Westbrook2013] until the indifference point is reached.
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see figure 1).
Additionally, we will test our adapted paradigm in a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al., ...).
```{r fig1, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Exemplary visualisation of two response patterns. In the top half, the person has a clear preference for one of the three strategies. In the lower half, they have no clear preference and therefore show an inconsistent response pattern. This pattern can also be represented by our paradigm.", out.width="90%"}
include_graphics(here("99_Thinktank","other","Paradigm_Scheme_T2.png" ))
```
## 1.2 The present study

@@

Exploratorily, we want to investigate whether individual SVs are related to personality traits and how individual SVs of ER strategies relate to SVs of other tasks with different demand levels, namely *n*-back.

### 2022-02-10 06_Paper/ER-ED/method.Rmd
fertsch

colnames(SubjArousalView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")

@@

# figure
FigPilot1=ggplot2::ggplot(Ratings_view, aes(x = block, y = arousal))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("view_neu", "view_neg"),
                   labels = c("Neutral", "Negative"))+
  geom_jitter(size = 0.4)+
  labs(y = "Arousal Rating")

@@

@@

# figure
FigPilot2 <- ggplot2::ggplot(Ratings_reg, aes(x = block, y = arousal))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("view_neg", "distraction", "distancing", "suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Arousal Rating")

@@

# Figure to visualize effort ratings
# figure
FigPilot3 = ggplot2::ggplot(Ratings_reg, aes(x = block, y = effort))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("view_neg", "distraction", "distancing", "suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Effort Rating")
```

@@

The procedure described above was tested in a pilot study with $N=`r nrow(data_quest)`$ participants (`r length(which(data_quest$gender == 2))` female; age: $M = `r round(mean(data_quest[,"age"], na.rm = TRUE), digits = 1)`\text{ }\pm\text{ }SD = `r round(sd(data_quest[,"age"], na.rm = TRUE), digits = 1)`$).
Results showed significant higher subjective (... and physiological ?!) arousal for active viewing of negative pictures, compared to active viewing of neutral pictures.

>>>>

colnames(SubjArousalView_con) <- c("Contrast", "Estimate", "$SE$", "$df$", "$t$", "$p$", "$BF10$", "$\\eta_{p}^{2}$", "$95\\% CI$")
# rename contrast for table
SubjArousalView_con[1,1] <- "$View_{negative} - View_{neutral}$"

@@

# figure
FigSubjArousalViewPilot=ggplot2::ggplot(Ratings_view, aes(x = block, y = arousal))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Active viewing", 
                   limits = c("view_neu", "view_neg"),
                   labels = c("Neutral", "Negative"))+
  geom_jitter(size = 0.4)+
  labs(y = "Arousal Rating")

@@

SubjArousalReg_con[1,1] <- "$Distancing - Distraction$"
SubjArousalReg_con[2,1] <- "$Distancing - Suppression$"
SubjArousalReg_con[3,1] <- "$Distancing - View_{negative}$"
SubjArousalReg_con[4,1] <- "$Distraction - Suppression$"
SubjArousalReg_con[5,1] <- "$Distraction - View_{negative}$"
SubjArousalReg_con[6,1] <- "$Suppression - View_{negative}$"

@@

# figure
FigSubjArousalRegPilot <- ggplot2::ggplot(Ratings_reg, aes(x = block, y = arousal))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("view_neg", "distraction", "distancing", "suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Arousal Rating")

@@

SubjEffort_con[1,1] <- "$Distancing - Distraction$"
SubjEffort_con[2,1] <- "$Distancing - Suppression$"
SubjEffort_con[3,1] <- "$Distancing - View_{negative}$"
SubjEffort_con[4,1] <- "$Distraction - Suppression$"
SubjEffort_con[5,1] <- "$Distraction - View_{negative}$"
SubjEffort_con[6,1] <- "$Suppression - View_{negative}$"

# Figure to visualize effort ratings
# figure
FigSubjEffortPilot = ggplot2::ggplot(Ratings_reg, aes(x = block, y = effort))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("view_neg", "distraction", "distancing", "suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Effort Rating")
```

@@

The procedure described above was tested in a pilot study with $N=`r nrow(data_quest)`$ participants (`r length(which(data_quest$gender == 2))` female; age: $M = `r round(mean(data_quest[,"age"], na.rm = TRUE), digits = 1)`\text{ }\pm\text{ }SD = `r round(sd(data_quest[,"age"], na.rm = TRUE), digits = 1)`$).
Results showed significant higher subjective (... and physiological ?!) arousal for active viewing of negative pictures, compared to active viewing of neutral pictures.
However, ER strategies could not reduce subjective arousal compared to active viewing of negative pictures.
Yet we found accordance with our previous studies [@Scheffel2021] that the use of ER strategies compared to active viewing was associated with increased subjective effort.
